\documentclass[10pt, a4paper]{cvhari}
\geometry{left=1.2cm,right=1.2cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=1.2cm,bottom=1.2cm}
\usepackage[default]{lato}
\begin{document}

%% Available on https://github.com/haribkurup/resume-template
%% Intentionally kept long, remove unwanted sections based on need or add new sections.
%% Derived from https://www.overleaf.com/latex/templates/recreating-business-insiders-cv-of-marissa-mayer/gtqfpbwncfvp

% % % Change your name, email ID, contact and LinkedIn URL here.
\name{Christian Gutermann} 
\tagline{Software Engineer $\bullet$ Scrum Master} % 
\personalinfo{%
    \email{christian.gutermann95@gmail.com}
    \phone{+49-1719308925}
    \location{Bruchsal, Germany}
    \vspace{0.8em}

    \linkedin{linkedin.com/in/chrisguter}
    \homepage{chrisguter.com}
}
\makecvheader
\medskip



% % % Your profile - What you ARE?
\cvsection{Profile}
    \par
    I’m a Scrum Master and Software Engineer who enjoys balancing hands-on coding with leading projects and teams. In my dual role, I help keep development moving smoothly by making sure everyone’s aligned, priorities are clear, and communication flows between stakeholders and engineers. I’m passionate about building useful, user-friendly products while also making sure the team stays focused, motivated, and on track.
    \par
\medskip


% % % Professional Experience - Reverse chronological and company/project specific information of what you did.
\cvsection{Professional Experience}

    \company
        {CAS Software AG}
        {SCRUM Master \& Software Engineer}
        {Karlsruhe, Germany}
        {September 2015 -- Present}
    \vspace{0.5em}

    \textbf{Scrum Master \& Software Engineer, Appfactory} \hfill \textbf{May 2021 -- Present}

    \vspace{0.2em}

    \begin{itemize}
        \item Stepped into the role of Scrum Master for a newly formed team, guiding them through agile methodologies and establishing a strong foundation for collaboration and delivery.

        \item Simultaneously contributed as a Software Engineer, staying closely involved with day-to-day development to better understand the team’s technical needs and challenges.

        \item Built and scaled an international team from 4 developers to 8 developers, 2 working students, and 1 QA tester — with team members based in Germany and Hungary.

        \item Conducted all team communication in English to support smooth cross-border collaboration.

        \item Fostered team cohesion and ensured consistent progress toward project goals.

        \item Created and maintained project roadmaps to align development efforts with business objectives, and regularly presented them to the head of the department to ensure strategic alignment and transparency.

        \item Involved in direct contact with customers from the start of projects to gather requirements and ensure their technical needs were clearly understood and addressed.

        \item Successfully shipped multiple projects to customers and currently manage over 10 active projects, including work for key clients such as Bioland, Daimler Truck, and Deutsche Bahn Energie.

        \item Monitored project budgets to ensure financial alignment and efficient resource use.

        \item Acted as a key communication bridge between development teams and stakeholders, ensuring transparency, clarity, and timely updates.

        \item Facilitated all Scrum ceremonies including daily stand-ups, sprint planning, retrospectives, and sprint reviews.

        \item Regularly moderated departmental sessions such as cross-team reviews to promote alignment and shared understanding across the organization.
        

    \end{itemize}

\smallskip
\divider
\smallskip
%\clearpage

    \textbf{Software Engineer, Appfactory} \hfill \textbf{May 2020 -- May 2021}

    \vspace{0.2em}
    \begin{itemize}
        \item Contributed to a variety of frontend projects, primarily using Angular, with a strong focus on modern web application development.

        \item Regularly utilized Docker for environment virtualization and maintained CI/CD pipelines to streamline development and deployment workflows.

        \item Acted as a mentor to several new team members, supporting onboarding and knowledge transfer.

        \item Transitioned from a German-speaking team to an international, cross-functional team, adapting to new communication styles and cultural dynamics.

        \item Took on additional responsibilities as substitute Scrum Master, facilitating agile ceremonies and supporting team organization in the absence of the dedicated Scrum Master.

        \item Voluntarily transferred departments to engage with innovative technologies and projects, demonstrating adaptability and initiative.

    \end{itemize}


\smallskip
\divider
\smallskip

    \textbf{Software Engineer, Education} \hfill \textbf{October 2018 -- May 2020}

    \vspace{0.2em}
    \begin{itemize}
         
        \item Launched career in software engineering with a focus on full-stack development, building and maintaining both front-end and back-end components for web-based applications.

        \item Designed and implemented user-friendly web interfaces, while also working on backend logic and database interactions to support robust system functionality.

        \item Gained practical experience with programming languages such as C\#, Java, and ASP, laying the foundation for enterprise-level software development.

        \item Specialized in developing student management systems tailored for higher education institutions, supporting administrative processes, enrollment, grading, and student communication.

        \item Played a key role in modernizing the department\'s technology stack, introducing updated frameworks and tools that improved performance and delivered a more intuitive user interface.

        \item Discovered a strong interest in frontend development, particularly with Angular, leading to deeper involvement in UI/UX design and interactive web components.

        \item Took initiative in team coordination by regularly leading smaller team ceremonies, including daily stand-ups, retrospectives, and other agile practices, helping improve communication and workflow.

\end{itemize}

\smallskip
\divider
\smallskip

    \textbf{Software Engineer, Education (Student)} \hfill \textbf{September 2015 -- October 2018}

    \vspace{0.2em}
    \begin{itemize}
        \item Completed an intensive 3-year dual study program (210 ECTS), combining academic coursework with practical on-the-job training in software development

        \item Gained hands-on experience through continuous integration into real-world development teams, applying classroom theory directly to live projects

        \item Focused on developing scalable software solutions and working within agile development environments from early on

        \item Took an active role in quality assurance, including writing and executing test cases, reporting bugs, and supporting release readiness

        \item Independently researched, selected, and implemented a new UI test automation framework, replacing a costly licensed tool and saving the company several thousand dollars annually; the solution remains in production use

        \item Authored a bachelor thesis titled "Creating a prototype of a framework for Angular apps embedded in SmartWe," developing a foundational tool for integrating Angular components into a modular CRM platform
    \end{itemize}
\medskip

\cvsection{Skills} 
    \bigskip
    \begin{minipage}[t]{0.23\textwidth}
            \centering
            \underline{\textbf{Frameworks}}\\[0.5em]
            Angular\\
            React\\
            Docker\\
            Scrum\\
            Vaadin\\
    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.23\textwidth}
            \centering
            \underline{\textbf{Languages}}\\[0.5em]
            German\\
            English\\
            TypeScript\\
            Java\\
            SQL\\
    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.23\textwidth}
            \centering
            \underline{\textbf{Tools}}\\[0.5em]
            Git\\
            Jenkins\\
            Jira\\
            Figma\\
            Confluence\\
    \end{minipage}
    \hfill
    \begin{minipage}[t]{0.23\textwidth}
            \centering
            \underline{\textbf{Soft Skills}}\\[0.5em]
            Communication\\
            Leadership\\
            Moderation\\
            Problem Solving\\
            Adaptability\\
    \end{minipage}
\medskip

\cvsection{Education}
\medskip
\education
    {Bachelor of Science in Computer Science}
    {Duale Hochschule Baden-Württemberg Karlsruhe} 
    {Karlsruhe, Germany}
    {2015 -- 2018}
    \par
    \dividergray
    
    \education
    {High School Diploma (Abitur)}
    {IGS Ludwigshafen-Oggersheim}
    {Ludwigshafen, Germany}
    {2006 -- 2015}

    \par
    \dividergray
\medskip

\cvsection{Bachelor Thesis Advisor} 
    \bigskip
    
    \cvachievement{\faBook}{ 
        {\bfseries Evaluation and Implementation of a Digitally Sovereign Solution to Increase Usage Transparency} \par
        {\bfseries of Web-Based Software Products} \hfill { \color{accent} \faCalendar}  \hspace{0.5em}{2024}
        \smallskip
    }
    {Duale Hochschule Baden-Württemberg Karlsruhe}\par
    
    \smallskip 
    \dividergray
    \smallskip
    
    \cvachievement{\faBook}{ 
        {\bfseries TBD} \hfill { \color{accent} \faCalendar}  \hspace{0.5em}{2021}
        \smallskip
    }
    {Duale Hochschule Baden-Württemberg Karlsruhe}\par
    \medskip

\medskip

\cvsection{Personal Interests} 
    \bigskip

    \begin{center}
        \begin{minipage}{0.18\textwidth}
            \centering
            \faGamepad\\
            \textbf{E-Sport}
        \end{minipage}
        \hfill
        \raisebox{-2.7em}{%
            \begin{minipage}{0.18\textwidth}
                \centering
                \faPaw\\
                \textbf{Dog training}
            \end{minipage}
        }
        \hfill
        \begin{minipage}{0.18\textwidth}
            \centering
            \faCutlery\\
            \textbf{Cooking}
        \end{minipage}
        \hfill
        \raisebox{-2.7em}{%
            \begin{minipage}{0.18\textwidth}
                \centering
                \faTree\\
                \textbf{Hiking}
            \end{minipage}
        }
        \hfill
        \begin{minipage}{0.18\textwidth}
            \centering
            \faMusic\\
            \textbf{Guitar}
        \end{minipage}
    \end{center}
    
\end{document}



